Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-12-11 analysis/cause-table.tex
Add the rendered causes table with column removed

% Fri Nov  7 16:47:38 2014
Time series & Population & ID & citation & Verified & Description & Pr($\nu < 10$ & $\widehat{\nu}$ \\ 

@@

\includegraphics[width=1.7cm]{../analysis/sparks/6528.pdf} & Shag, \textit{Phalacrocorax aristotelis}, Farne Islands, Northumberland & 6528 & \citep{potts1980} & yes & red tide & 1.00 & 2.4 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/7115.pdf} & South African fur seal, \textit{Arctocephalus pusillus}, South Africa & 7115 & \citep{shaughnessy1982} & yes? & harvesting and predation changes & 1.00 & 2.5 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10128.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Scotland - un-named area & 10128 & \citep{potts1984} & yes & environmental- and parisitic-caused cycles & 1.00 & 2.6 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9382.pdf} & Pine looper or Bordered white, \textit{Bupalus piniaria}, Kessock & 9382 & \citep{broekhuizen1993} & yes &  & 1.00 & 2.7 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10127.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Scotland - un-named area & 10127 & \citep{potts1984} & yes & environmental- and parisitic-caused cycles & 0.99 & 2.7 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10007.pdf} & Water vole, \textit{Arvicola terrestris}, Le Pont & 10007 & \citep{saucy1994} & yes & predator-environment cycle interactions & 1.00 & 2.7 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/20579.pdf} & Grey heron, \textit{Ardea cinerea}, Southern Britain & 20579 & \citep{stafford1971} & yes? & severe winter & 0.98 & 3.0 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9655.pdf} & Flea beetle, \textit{Chaetocnoma concinna}, Finland & 9655 & \citep{markkula1965} &  &  & 0.99 & 3.0 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/1235.pdf} & Wren, \textit{Troglodytes troglodytes}, Eastern Wood, Bookham Common & 1235 & \citep{newton1998} & yes? & severe winter & 0.98 & 3.0 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10113.pdf} & Willow grouse, \textit{Lagopus lagopus}, Northern England & 10113 & \citep{dobson1995} & yes? & parasites and predators & 0.99 & 3.1 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9667.pdf} & Gooseberry sawfly, \textit{Nemastus ribesii}, Finland & 9667 & \citep{markkula1965} &  &  & 0.97 & 3.2 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9679.pdf} & Unknown, \textit{Trioza apicalis}, Finland & 9679 & \citep{markkula1965} &  &  & 0.83 & 3.4 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/20527.pdf} & Wandering albatross, \textit{Diomedea exulans}, Taiaroa & 20527 & \citep{robertson1998} & IN LIBRARY &  & 0.99 & 3.5 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10039.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Northern Scotland & 10039 & \citep{dobson1995} & yes & parasites and predators & 0.92 & 3.9 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10162.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Atholl Estate & 10162 & \citet{mackenzie1952} & yes & overcrowding and environemnt & 0.91 & 4.6 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9503.pdf} & Fisher or  Pekan, \textit{Martes pennanti}, Manitoba & 9503 & \citep{keith1963} & IN LIBRARY &  & 0.76 & 4.8 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/7099.pdf} & European rabbit, \textit{Oryctolagus cuniculus}, Estate 2, East Anglia & 7099 & \citep{barnes1986} & yes & disease outbreak followed by years of good weather & 0.78 & 4.8 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/2778.pdf} & Wheatear, \textit{Oenanthe oenanthe}, Skokholm Island & 2778 & \citep{lack1969} & yes & unknown, but decline noted specifically, cold winters later & 0.67 & 5.3 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9659.pdf} & Cabbage root fly or maggot, \textit{Delia radicum}, Finland & 9659 & \citep{markkula1965} &  &  & 0.59 & 6.8 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/1195.pdf} & Blue jay, \textit{Cyanocitta cristata}, Robert Allerton Park & 1195 & \citep{kendeigh1982} & yes & unknown & 0.60 & 6.9 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/5019.pdf} & Barbary macaque, \textit{Macaca sylvanus}, Queens Gate & 5019 & \citep{fa1984} &  &  & 0.61 & 6.9 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9953.pdf} & Rock ptarmigan, \textit{Lagopus mutus}, Iceland & 9953 & \citep{clarke1885,williams1954} &  & severe winters & 0.58 & 7.2 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/6548.pdf} & Lesser-spotted dogfish, \textit{Scyliorhinus caniculus}, North Sea & 6548 & \citep{heessen1996} & yes & unknown & 0.53 & 8.5 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/20546.pdf} & American red fox, \textit{Vulpes fulva}, Labrador & 20546 & \citep{dancona1954,lindstrom1994} & yes & predator-prey cycles & 0.57 & 8.7 \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9470.pdf} & Ruffed grouse, \textit{Bonasa umbellus}, Connecticut & 9470 & \citep{keith1963} & IN LIBRARY &  & 0.53 & 8.9 \\ 

>>>>

Time series & Population & ID & Citation & Description & Pr($\nu < 10$) & $\widehat{\nu}$ \\ 

@@

\includegraphics[width=1.7cm]{../analysis/sparks/6528.pdf} & Shag, \textit{Phalacrocorax aristotelis}, Farne Islands, Northumberland & 6528 & \citep{potts1980} & Red tide event combined with low productivity due to overcrowding & 1.00 & 2 (2--4) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/7115.pdf} & South African fur seal, \textit{Arctocephalus pusillus}, South Africa & 7115 & \citep{shaughnessy1982} & Harvesting and predation changes & 1.00 & 2 (2--4) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10128.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Scotland - un-named area & 10128 & \citep{potts1984} & Environment- and parisite-caused cycles & 1.00 & 3 (2--4) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9382.pdf} & Pine looper or Bordered white, \textit{Bupalus piniaria}, Kessock & 9382 & \citep{broekhuizen1993} & Unknown, but sampling intensity was decreasing & 1.00 & 3 (2--5) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10127.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Scotland - un-named area & 10127 & \citep{potts1984} & Environment- and parisite-caused cycles & 0.99 & 3 (2--5) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10007.pdf} & Water vole, \textit{Arvicola terrestris}, Le Pont & 10007 & \citep{saucy1994} & Predator-environment cycle interactions & 1.00 & 3 (2--5) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/20579.pdf} & Grey heron, \textit{Ardea cinerea}, Southern Britain & 20579 & \citep{stafford1971} & Severe winter & 0.98 & 3 (2--7) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9655.pdf} & Flea beetle, \textit{Chaetocnoma concinna}, Finland & 9655 & \citep{markkula1965} & Cannot locate original source & 0.99 & 3 (2--6) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/1235.pdf} & Wren, \textit{Troglodytes troglodytes}, Eastern Wood, Bookham Common & 1235 & \citep{newton1998} & Severe winter & 0.98 & 3 (2--8) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10113.pdf} & Willow grouse, \textit{Lagopus lagopus}, Northern England & 10113 & \citep{dobson1995} & Parasites and predators & 0.99 & 3 (2--6) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9667.pdf} & Gooseberry sawfly, \textit{Nemastus ribesii}, Finland & 9667 & \citep{markkula1965} & Cannot locate original source & 0.97 & 3 (2--8) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9679.pdf} & Unknown, \textit{Trioza apicalis}, Finland & 9679 & \citep{markkula1965} & Cannot locate original source & 0.83 & 3 (2--88) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/20527.pdf} & Wandering albatross, \textit{Diomedea exulans}, Taiaroa & 20527 & \citep{robertson1998} & Unknown & 0.99 & 4 (2--7) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10039.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Northern Scotland & 10039 & \citep{dobson1995} & Parasites and predators & 0.92 & 4 (2--12) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/10162.pdf} & Red grouse, \textit{Lagopus lagopus scoticus}, Atholl Estate & 10162 & \citet{mackenzie1952} & Bad environmental conditions and overcrowding combined to create crashes & 0.91 & 5 (2--12) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9503.pdf} & Fisher or  Pekan, \textit{Martes pennanti}, Manitoba & 9503 & \citep{keith1963} & Unknown & 0.76 & 5 (2--87) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/7099.pdf} & European rabbit, \textit{Oryctolagus cuniculus}, Estate 2, East Anglia & 7099 & \citep{barnes1986} & Disease outbreak followed by years of good weather & 0.78 & 5 (2--67) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/2778.pdf} & Wheatear, \textit{Oenanthe oenanthe}, Skokholm Island & 2778 & \citep{lack1969} & Unknown, but decline noted specifically, cold winters caused some crashes & 0.67 & 5 (2--141) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9659.pdf} & Cabbage root fly or maggot, \textit{Delia radicum}, Finland & 9659 & \citep{markkula1965} & Cannot locate original source & 0.59 & 7 (2--161) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/1195.pdf} & Blue jay, \textit{Cyanocitta cristata}, Robert Allerton Park & 1195 & \citep{kendeigh1982} & Unknown & 0.60 & 7 (2--149) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/5019.pdf} & Barbary macaque, \textit{Macaca sylvanus}, Queens Gate & 5019 & \citep{fa1984} & Cannot locate original source & 0.61 & 7 (2--132) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9953.pdf} & Rock ptarmigan, \textit{Lagopus mutus}, Iceland & 9953 & \citep{clarke1885,williams1954} & Severe winters & 0.58 & 7 (2--172) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/6548.pdf} & Lesser-spotted dogfish, \textit{Scyliorhinus caniculus}, North Sea & 6548 & \citep{heessen1996} & Unknown, not specifically mentioned & 0.53 & 8 (2--190) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/20546.pdf} & American red fox, \textit{Vulpes fulva}, Labrador & 20546 & \citep{dancona1954,lindstrom1994} & Predator-prey cycles & 0.57 & 9 (3--65) \\ 
  \includegraphics[width=1.7cm]{../analysis/sparks/9470.pdf} & Ruffed grouse, \textit{Bonasa umbellus}, Connecticut & 9470 & \citep{keith1963} & Unknown & 0.53 & 9 (3--158) \\ 
